\vfill World of Warcraft's New Way to Get You Hooked

### 2013-02-13 paper.tex
I like this abstract slightly better.

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
World of Warcraft has a ``Starter Edition'' allowing players access for free indefinitely with restrictions. \cite{starterEditionNewsRelease} Studies show a correlation between time playing and addiction to Massively Multiplayer Online Role-Playing Games (MMORPGs) like World of Warcraft. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} Is it ethical for World of Warcraft to use this model?

Based on the principles of Utilitarianism \cite{Utilitarianism}, restricting a free demo on the basis of a few scattered cases of mental instability is unethical, therefore World of Warcraft's ``Starter Edition'' \emph{is} ethical.
\end{abstract}

>>>>

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
World of Warcraft uses a ``Starter Edition'' which allows players access for free indefinitely with restrictions. \cite{starterEditionNewsRelease} Studies show a correlation between time playing and addiction to Massively Multiplayer Online Role-Playing Games (MMORPGs) like World of Warcraft. \cite{ProblemUsageAmongHighlyEngagedPlayers}\cite{JustAComputerGameRight} Is it ethical for World of Warcraft to use this model?

Based on the principles of Utilitarianism \cite{Utilitarianism}, restricting a free demo on the basis of a few cases of mental instability is unethical, therefore World of Warcraft's ``Starter Edition'' \emph{is} ethical.
\end{abstract}
